%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Adam Petrovic 
\documentclass[margin,line]{resume}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Adam Petrovic}
\vspace{2mm}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    mobile: +61 400 077 049          \vspace{0mm}\\\vspace{0mm}%
    website: \href{http://www.adampetrovic.me}{adampetrovic.me}		\vspace{0mm}\\\vspace{0mm}%
    e-mail: \href{mailto:me@adampetrovic.me}{me@adampetrovic.me}	  \vspace{0mm}\\\vspace{-4.5mm}%
    
    \vspace{2mm}

    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Related\\Interests}

    Programming, Cloud Computing, Distributed Systems, API Development, Queueing Systems


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{The University Of Sydney}, Camperdown, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Information Technology (Computer Science)} \hfill \textbf{January 2008 -- July 2012}\vspace{-3mm}\\\vspace{-1mm}%
     \begin{list2}
	\item Honour Roll for Distinction Average in IT (2008 -- 2010)
	\item Treasurer of the Sydney University IT Society (2009 / 2010)
	\item Treasurer of the Sydney University IT Society (2010 / 2011)
     \end{list2}\vspace{-1.5mm}

    \textbf{Newington College}, Stanmore, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Higher School Certificate} \hfill \textbf{February 2004 -- December 2007}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Full College Prefect 
        \item Metcalfe House Honour Colours
	\item 1st Grade Football
	\item 3rd Grade GPS Representative Football 
    \end{list2}\vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Honours and Awards
    %\section{\mysidestyle Honours and\\Awards} 

    %Best Paper Award, Griffith School of Engineering Research Conference, Nathan, 2007              \vspace{1mm}\\%
    %Australian Research Council (ARC) Postgraduate Research Scholarship, Nathan, 2005-2010          \vspace{1mm}\\%
    %Scholarship for Outstanding Academic Achievement, Griffith University, Nathan, 2000             \vspace{1mm}\\%
    %National Mathematics Summer School, The Australian National University, Canberra, 2000, 1999    \vspace{1mm}\\%
    %Certificate of Excellence for Outstanding Academic Achievement, University of Tasmania, 1999    \vspace{1mm}\\%
    %Award for Best Design, Electronics Competition, The Electronics Educators Association, 1998 


    %__________________________________________________________________________________________________________________
    % Publications
    %\section{\mysidestyle Selected Publications}

    %Paliwal, K.K., Shannon, B.J., Lyons, J.G. and K.K. W\'ojcicki,
    %``Speech-signal-based frequency warping'',
    %\textsl{IEEE Signal Process. Lett.}, Vol. 16, No. 4, pp. 319-322, 2009.

%\vspace{-2mm}
%    Paliwal, K.K. and K.K. W\'ojcicki,
%    ``Effect of analysis window duration on speech intelligibility'',
%    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 785-788, 2008.

%\vspace{-2mm}
%    Stark, A.P., W\'ojcicki, K.K., Lyons, J.G. and K.K. Paliwal,
%    ``Noise driven short time phase spectrum compensation procedure for speech enhancement'',
%    In \textsl{Proc. INTERSPEECH}, pp. 549-552, 2008.

%\vspace{-2mm}
%    W\'ojcicki, K.K., Milacic, M., Stark, A.P., Lyons, J.G. and K.K. Paliwal,
%    ``Exploiting conjugate symmetry of the short-time Fourier spectrum for speech enhancement'',
%    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 461-464, 2008.

%\vspace{-2mm}
%    W\'ojcicki, K.K. and K.K. Paliwal,
%    ``Importance of the dynamic range of an analysis window function for phase-only and magnitude-only reconstruction of speech'',
%    In \textsl{Proc. ICASSP}, pp. 729-733, 2007.



    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{Freelancer.com}, Vancouver, BC, Canada \& Sydney, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Infrastructure Engineer} \hfill \textbf{January 2014 -- present}\\
    Involved with leading a team of infrastructure engineers in the development of multiple micro-services. As part of this task, our team 
    spearheaded the integration of production-critical technologies such as RabbitMQ, Thrift and ElasticSearch. In addition to development,
    I have been heavily involved in defining the company's usage of AWS and how production servers are provisioned and deployed.
    
        After Freelancer's hugely successful IPO on the ASX, I was promoted and tasked with the role of setting up and coordinating
    the engineering operations in their new North American engineering lab based in Vancouver, Canada. This role includes the 
    recruitment, training and management of a team of Systems Engineers, DevOps Engineers and Infrastructure Engineers reporting directly
    to the Vice President of Engineering.

    \textbf{Freelancer.com}, Pyrmont, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Infrastructure Engineer} \hfill \textbf{August 2011 -- January 2014}\\
    Responsible for the creation of numerous backend service APIs (Authentication, Secure Fileservice, Notifications and Messaging),
    and the improvement of the company's infrastructure processes with the introduction of systems such as
    RabbitMQ and Thrift. The various systems I have built for Freelancer.com range in implementation in Python, Golang and PHP.
    Other systems include the creation of a custom Gamification system and a persistence layer for realtime notifications. 
    In addition to feature development for the website, I was heavily involved with the implementation and development of DevOps systems. 
    These systems include the integration of Git from SVN, GitLab, Sentry and the creation of development environments using Puppet and Vagrant.
   
    \textbf{The University Of Sydney}, Camperdown, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Tutor (Software Development Project Advanced)} \hfill \textbf{July 2011 -- December 2011}\\
    Assisting students with the various aspects of managing a team in a software development environment.
    This role includes a knowledge of the various aspects of ``Extreme Programming'' as well as other development
    methodologies such as Test Driven Development and Pair Programming.

    \textbf{DarkByte Pty. Ltd.}, Sydney, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Web Application Developer - Casual} \hfill \textbf{April 2011 -- January 2012}\\
    Small Business server deployment, software development solutions including E-Commerce applications,
    newsletter management systems and custom business processing software.	

\newpage

    \textbf{Fairscan Pty. Ltd.}, Sydney, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Field Hardware and Software Technician - Casual} \hfill \textbf{January 2010 -- January 2012}\\
    Point-of-sale deployments for over 120 small business clients at trade fairs. Support technician for various Windows
    related issues arising from the use of these systems.

    \textbf{Petrovic Design}, Sydney, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Web Designer \& Developer} \hfill \textbf{January 2007 -- March 2011}\\
    Self-employed web designer and developer. Main jobs were websites and web-based solutions for small business clients.
    This involved writing accounts / inventory management software amongst a number of other solutions to improve the day
    to day running of small business.

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming and Tools} 

    Python, Golang, UNIX, PHP, SQL, jQuery, Javascript, HTML \& CSS, Git, MySQL, RabbitMQ, Apache Thrift, Flask, \LaTeXe.

    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}


\vspace{5mm}
\section{\mysidestyle Sport}
	
	\textbf{Elite Referee's Development Panel}, Parklea, NSW, Australia \vspace{2mm}\\\vspace{1mm}%
	\textsl{Football Referee} \hfill \textbf{March 2005 -- December 2011}\\
	Member of the Elite Development Panel, a small group of Football (Soccer) referees who are chosen by Football NSW
	to referee the respresentative matches throughout the state.


%______________________________________________________________________________________________________________________
\section{\mysidestyle Referees} 

Available upon request.
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

